Insert title of project here

### 2022-04-18 Draft Report/Draft Project.Rmd
Added EJSCreen code and Filtered CSV's (see line 162 and then 200/225/250)

@@

# See GEOID Structure, <https://www.census.gov/programs-surveys/geography/guidance/geo-identifiers.html> all the other stuff is Census Tracts not BlockGroups
names(EJ_California)[names(EJ_California) == 'ID'] <- 'BLOCKID'
EJ_California <- EJ_California %>%
  mutate(TRACTID = as.double(substr(EJ_California$BLOCKID,1,10)))

@@

EJScreen_Florida <- EJ_Florida
names(EJScreen_Florida)[names(EJScreen_Florida) == 'ID'] <- 'BLOCKID' 
EJScreen_Florida <- EJScreen_Florida %>% mutate(TRACTID = as.double(substr(EJScreen_Florida$BLOCKID,1,11)))

@@

EJScreen_norcar <- EJ_NorCar
names(EJScreen_norcar)[names(EJScreen_norcar) == 'ID'] <- 'BLOCKID' 
EJScreen_norcar <- EJScreen_norcar %>% mutate(TRACTID = as.double(substr(EJScreen_norcar$BLOCKID,1,11)))

@@

>>>>

## COMMENT THESE OUT THEN READ THEM IN
write.table(EJ_California,'./Potential Data Sources/Census Tracts/EJScreen_California.csv',col.names=TRUE,sep=",")
write.table(EJ_NorCar,'./Potential Data Sources/Census Tracts/EJScreen_NorthCarolina.csv',col.names=TRUE,sep=",")
write.table(EJ_Florida,'./Potential Data Sources/Census Tracts/EJScreen_Florida.csv',col.names=TRUE,sep=",")
###

@@

# See GEOID Structure, <https://www.census.gov/programs-surveys/geography/guidance/geo-identifiers.html> all the other stuff is Census Tracts not BlockGroups
# READ IN THE CSV FILE FOR './Potential Data Sources/Census Tracts/EJScreen_California.csv'
# READ IN THE CSV FILE FOR './Potential Data Sources/Census Tracts/EJScreen_California.csv'
# READ IN THE CSV FILE FOR './Potential Data Sources/Census Tracts/EJScreen_California.csv'
names(EJ_California)[names(EJ_California) == 'ID'] <- 'BLOCKID'
EJ_California <- EJ_California %>%
  mutate(TRACTID = as.double(substr(EJ_California$BLOCKID,1,10)))

@@

# READ IN THE CSV FILE FOR './Potential Data Sources/Census Tracts/EJScreen_Florida.csv'
# READ IN THE CSV FILE FOR './Potential Data Sources/Census Tracts/EJScreen_Florida.csv'
# READ IN THE CSV FILE FOR './Potential Data Sources/Census Tracts/EJScreen_Florida.csv'
EJScreen_Florida <- EJ_Florida
names(EJScreen_Florida)[names(EJScreen_Florida) == 'ID'] <- 'BLOCKID' 
EJScreen_Florida <- EJScreen_Florida %>% mutate(TRACTID = as.double(substr(EJScreen_Florida$BLOCKID,1,11)))

@@

# READ IN THE CSV FILE FOR './Potential Data Sources/Census Tracts/EJScreen_NorthCarolina.csv'
# READ IN THE CSV FILE FOR './Potential Data Sources/Census Tracts/EJScreen_NorthCarolina.csv'
# READ IN THE CSV FILE FOR './Potential Data Sources/Census Tracts/EJScreen_NorthCarolina.csv'
EJScreen_norcar <- EJ_NorCar
names(EJScreen_norcar)[names(EJScreen_norcar) == 'ID'] <- 'BLOCKID' 
EJScreen_norcar <- EJScreen_norcar %>% mutate(TRACTID = as.double(substr(EJScreen_norcar$BLOCKID,1,11)))

@@

mapview(list(NC_NRI_fire_shp,NC_EJ_shp),
        zcol=c("WFIR_RISKS","PRE1960PCT"),
        layer.name=list("Fire Risk","Relative Building Ages"))
